\white{Douglas Tournament Overview: (October 26, 2024)}
\chapterauthor{Caleb Bachmeier}
\info{October 26, 2024}{Douglas Tournament Overview}{Caleb Bachmeier}
\textbf{Goal:} Analyze the tournament in Douglas, South Dakota
\section*{General Tournament Information}
\begin{itemize}
    \item \textbf{Tournament Name:} DOUGLAS PATRIOTS High Stakes
    \item \textbf{Date:} 26th of October, 2024
    \item \textbf{Location:} Douglas, South Dakota
    \item \textbf{Winning Teams:} 7686A  - 6844B
\end{itemize}

\section*{Performance Information}
\begin{itemize}
    \item \textbf{Record for Qualification Matches}: 4/4/0 50\% win percentage
    \item \textbf{Alliance Selection:} 82728B
    \item \textbf{Finals:} We lost in semifinals
\end{itemize}
\subsection*{Qualification: 4}

\begin{itemize}
    \item \textbf{Blue Alliance:} 82718E - 7686H
    \item \textbf{Red Alliance:} 89910A - 7686X
    \item \textbf{Score:} \colorbox{cyan}{27} \colorbox{red}{11}
    \item \textbf{Autonomous Winner: Blue}
    \item \textbf{Our Strategy}: We planned to have Chase and Miles to fill up as many Mobile Goals as they can. During this, we would have our teammates, 89910A, sit in the Positive Corner until we gave them a filled Mobile Goal to put into the corner. 
    \item \textbf{How the match went}: When the Autonomous Period started, our robot just started spinning around and didn't score any points. When we started Driver Control teammates went into the Positive Corner, like they should've, but once they were in there, their robot had a fatal error and couldn't move. Also once we had three Rings on a Mobile Goal, a Ring fell off our Intake, and into the inner workings of the robot, this prevented us from scoring any more Rings on a Mobile Goal.
    \item \textbf{What We Can Learn:} Having a good backup plan will be very useful in the future. We aren't sure on what happened with our Autonomous program, but we can figure that out.
\end{itemize}

\subsection*{Qualification: 10}

\begin{itemize}
    \item \textbf{Blue Alliance:} 7686X - 7686N
    \item \textbf{Red Alliance:} 9050E - 99515A
    \item \textbf{Score: \colorbox{cyan}{12}
    \colorbox{red}{2}}
    \item \textbf{Autonomous Winner:} Tie
    \item \textbf{How the match went}: Autonomous: Nobody's robot did anything during autonomous.. Driver: we quickly put two three Ring, Mobile Goals into the Positive corners, this remained consistent until 9050E clamped onto our Positive corner within the protected period, disqualifying them. Then we went over and grabbed the Mobile Goal and put it in the Positive corner - illegally. This disqualified us technically losing us the match.
\end{itemize}

\subsection*{Qualification: 13}

\begin{itemize}
    \item \textbf{Blue Alliance:} 9050B - 7686X
    \item \textbf{Red Alliance:} 89910A - 82718G
    \item \textbf{Score: \colorbox{cyan}{20} \colorbox{red}{0}}
    \item \textbf{Autonomous Winner:} Blue
    \item \textbf{Our Strategy}: Our strategy was the same as Qualification 4, have our teammates camp the positive corners, until we filled up a Mobile Goal to put in it.
    \item \textbf{How the match went}: We started off by scoring one Blue Ring on a Mobile Goal in the Autonomous period. Not as well as we'd like, but no other team on the field had a Autonomous program, so the Autonomous win was guaranteed. After Driver Control period started we filled up a Mobile Goal with five Blue Rings. We would like to get six rings, but we had an opportunity to place it in the Positive Corner, so we took it. But when we were placing it we high centered ourselves on a Ring, unfortunately this means we couldn't move anymore. Because of this we had our teammates help us guard the Mobile Goal in the corner. This worked very well because, although they tried, the Red Alliance couldn't score at all.
    \item \textbf{What We Can Learn}: 
\end{itemize}

\subsection*{Qualification: 27}

\begin{itemize}
    \item \textbf{Blue Alliance:} 6844B - 7686X
    \item \textbf{Red Alliance:} 6844E - 57437A
    \item \textbf{Score: \colorbox{cyan}{39} \colorbox{red}{3}}
    \item \textbf{Autonomous Winner:} Blue
    \item \textbf{How the match went}:We got two full Mobile Goals in the Positive corner after a successful Autonomous program. We had great coordination, 6844B might be a good Alliance partner
\end{itemize}

\subsection*{Qualification: 34}

\begin{itemize}
    \item \textbf{Blue Alliance:} 7686A - 7686X
    \item \textbf{Red Alliance:} 82718A - 99515B
    \item \textbf{Score: \colorbox{cyan}{29} \colorbox{red}{3}}
    \item \textbf{Autonomous Winner:} Blue
    \item \textbf{Our Strategy}: Autonomous was great both of ours worked and we got AWP. In driver we disconnected halfway through the match, we need to look into this

\end{itemize}

\subsection*{Qualification: 42}

\begin{itemize}
    \item \textbf{Blue Alliance:} 7686H - 99515C
    \item \textbf{Red Alliance:} 7686X - 57783B
    \item \textbf{Score: \colorbox{cyan}{8} \colorbox{red}{6}}
    \item \textbf{Autonomous Winner:} Tie
    \item \textbf{How the match went}: Autonomous: Our program didn't do anything, but nobody's else did anything either. Our Robot lost connection halfway through the match, leading to a grueling loss. 
\end{itemize}

\subsection*{Quarterfinals}
\begin{itemize}
    \item \textbf{Blue Alliance:} 7686N - 82718A
    \item \textbf{Red Alliance:} 82718B - 7686X
    \item \textbf{Score: \colorbox{cyan}{0} \colorbox{red}{22}}
    \item \textbf{Autonomous Winner:} Red
    \item \textbf{How the match went}:  We got two almost full Mobile Goals in each Positive corner. In the final seconds, we took Red's Mobile Goals and put them in the Negative Corner.
\end{itemize}
\subsection*{Semifinals}
\begin{itemize}
    \item \textbf{Blue Alliance:} 82718B - 7686X
    \item \textbf{Red Alliance:} 7686A - 6844B
    \item \textbf{Score: \colorbox{cyan}{2} \colorbox{red}{26}}
    \item \textbf{Autonomous Winner:} Red
    \item \textbf{How the match went}: Autonomous: everyone had a program that worked, we just lost. In driver the Red Alliance got both of their Mobile Goals in the Positive Corners. In the final protected period, 7686A took our two Mobile Goals and put them in the Negative Corners
\end{itemize}

\section*{Coding}
\subsection*{Pre-Tournament Preparation}
All code was working going into the tournament, minus a slight electrical issue with one of our drive motors that we noticed during our pre-tournament scrimmages. We started the day using two controllers, still keeping the switchable function enabled.

\subsection*{Early Matches and Initial Problem}
After two matches, both drivers decided that they no longer wanted the switchable feature. They encountered issues selecting the correct program before matches—mainly due to a buggy autonomous (auton) selector when switching between control loops.

In a rush to fix the code before the next match, I quickly applied what seemed to be the fastest solution. Without fully considering the long-term impact, I commented out the assignment of:
\begin{minted}[linenos, fontsize=\small]{cpp}
switch_button = pros::Controller::E_DIGITAL_B;
\end{minted}
\subsection*{Unexpected Issue with the Controller}
While this seemed to work momentarily, I overlooked an important detail: the default constructor for \texttt{switch\_button} within the \texttt{my\_controller} class was:
\begin{minted}[linenos, fontsize=\small]{cpp}
pros::Controller::E_DIGITAL_DOWN;
\end{minted}

During the next match, the robot stopped functioning entirely. Initially, we blamed field control for the issue. However, when the problem recurred across multiple matches, I suspected it was a programming issue—but I couldn’t recall making significant changes that would have caused it.

\subsection*{Finding the Bug and Implementing the Fix}
After some investigation and reviewing the code, I realized the problem: when the driver tried to use the mobile goal clamp, the controller was automatically switching from \texttt{master} to \texttt{slave}. However, the \texttt{slave} controller was not connected to field control or even present near the field.

The solution involved reinstating the switch button in the code and disabling the switching functionality entirely. This quick fix worked just in time for our next match.

\subsection*{Outcome and Lessons Learned}
Unfortunately, due to the bug, we lost three matches—largely due to an easy strength of schedule that could have been managed better without the issue. While the temporary fix solved the immediate problem, the experience highlighted the importance of thorough testing, even under time constraints.

\section*{Strategy Analysis}
\begin{itemize}
    \item \textbf{Overall Tournament Strategy:} [Summary of the General Tournament Strategy]
    \item \textbf{Strengths:} [Strengths of the Team and Robot]
    \item \textbf{Weaknesses:} [Weaknesses or Areas for Improvement]
    \item \textbf{Adaptability:} [How the Team Adapted to Opponents]
    \item \textbf{Key Matches:} [Analysis of Key Matches]
\end{itemize}

\section*{Lessons Learned}
\begin{itemize}
    \item \textbf{Technical Improvements:} [Ideas for Technical Improvements]
    \item \textbf{Strategic Adjustments:} [Adjustments to Strategy]
    \item \textbf{Preparation Tips:} [Tips for Future Preparation]
    \item \textbf{Overall Record For Douglas}: 4/4/0 50\%
    \item \textbf{Overall Record for High Stake}: 4/4/0 50\%
\end{itemize}
Our next tournament is in less than a week in Grand Forks, North Dakota.

