\white{Appendix B Preamble (October 28th, 2024)}
\chapterauthor{Ian Smith}
\info{Ian Smith}{Appendix B}{October 28th, 2024}

This appendix contains the code for every functionality in the engineering design process for the current robot. Some of the code is included to demonstrate the evolution of the design, but most of it is currently on the robot. In this appendix, you will find Jayden’s simulation code, Ian’s reinforcement learning code, and the robot functionality code.

It is recommended that you start by locating the \texttt{src/main.cpp} file. Read this file, and if you have any questions about the origins of the code, check the included headers and look through them to find the declarations.

Unfortunately, implementing this directly into the notebook is not very user-friendly. We have a GitHub repository, but it is my understanding that judges cannot view links while judging.

Over the several months of programming that went into this robot, many engineering design process (EDP) cycles have been run. Only the most notable ones are included in the notebook, as most of them would be repetitive. Prioritizing quality over quantity, we have chosen to exclude many entries.

Please also note that \texttt{VEX\_AI} is currently in a very early beta phase. We have completed the baseline implementation, but we haven’t had time to fully document it before the Grand Forks Signature Event. This notebook was printed on October 30, and we are finishing the implementation the day after printing. We will also be gathering media that day.

In summary, we will have \texttt{VEX\_AI} on the robot for the skills competition at the Grand Forks Signature Event, but it will not be documented. Enjoy reading through the next 3,969 lines of code!
